Analysis for Non-Expressive performances (DURATION)

### 2020-04-23 material/analysis/stim_n/ioi_duration.Rmd
export duration_seq csv
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

#### Sequence plot
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Non-Expression") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq
```

>>>>

#### Sequence plot
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]
# save data.table for comparison with stim_a
fwrite(duration_seq, file = "./seq.csv")

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Non-Expression") +
  scale_x_continuous(breaks=seq(1,66,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_duration_seq
```
